---
title: "Code Book"
author: "Lilith21971"
date: "5/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

This code book was created as part of the *Coursera/ Johns Hopkins University “Getting and Cleaning Data” Course Project*.

The purpose of the project is to demonstrate ability to collect, work with, and clean a data set.

The project consists on preparing a tidy data set for the **“Human Activity Recognition Using Smartphones Data Set”**, generating a second tidy data set with variables means and providing this code book.

The *run_analysis.R* script available in my GitHub repository (where you found this code book) performs the data preparation.


### Raw data

The “Human Activity Recognition Using Smartphones Data Set” presents data collected from features of Samsung Galaxy S smartphones in an experiment carried out with a group of 30 volunteers.

A broader description is available at:
[RawDataSetInformation](http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones)

The raw data used in the course project can be downloaded here: 
[RawData](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip)


### Actions performed to prepare the final tidy data set

Given the course project instructions, the *run_analysis.R* script performs the following steps:  
1. Downloads the raw data set  
2. Loads the data into R  
3. Merges the training and the test sets  
4. Extracts a subset containing only the measurements on the mean and standard deviation for each feature variable  
5. Uses descriptive activity names to name the activities in the merged data set  
6. Labels the data set with descriptive variable names  
      *- Uses capital letter at the beginning of words present in the names*  
      *- Replaces less intuitive abbreviations by extended words*  
      *- Deletes special characters*  
      *- Reorders parts of the names*  
7. Creates a second, independent, tidy data set with the average of each (feature measurement) variable within each pair of subject and activity  

Note: The *run_analysis.R* script includes various comments explaining the commands used.


### Tidy data

The final tidy data set is available in my GitHub repository as a text file *(FinalData.txt)*. To read it in R, after downloading it and properly addressing its path, run: read.table(“path/FinalData.txt”, header = TRUE).

**Dimensions (wide form):** 180 rows, 88 columns.

**Variables description:** All variables in the list below, except Subject and Activity, refer to group means, i.e. they are feature measurement averages within the pair of Subject and Activity.


```{r list_of_variables, echo=FALSE, warning=FALSE}
#library(rmarkdown)
#library(knitr)
library(xlsx)
library(kableExtra)

data <- read.xlsx("D:/Treinamento/CursosR/GettingAndCleaningData/Week4/scripts/Course_Project/Variables_list.xlsx", sheetIndex=1, header = TRUE) 

data %>% kable(caption='<b>List of Variables</b>', align=c("r", "l", "l", "l")) %>%
        kable_paper(fixed_thead=T) %>%
        footnote(general="All variables, except Subject and Activity, refer to group means, i.e. they are feature measurement averages within the pair of Subject and Activity.")
```

